---
title: "Lab 2"
author: 
- "Isaac Tetteh "
- "Joshua Edward Zimmerman"
- "Omar Taylor"
date: "February 1, 2018"
output: html_document
---
#### Reading data 
```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)

```

The total number of chocplate cars rated are 

```{r}
dim(choco)[1]

```

```{r}
library(ggplot2)
ggplot(data = choco, aes(x = Review.Date)) +
  geom_bar()

```
```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram(binwidth=0.4)

```

From the histogram above you can see that there are some outliers at about rating 5 and also almost left skewed.

```{r}
ggplot(choco, aes(x = Rating, y = Cocoa.Pct ,color=Rating)) + 
  geom_point() + geom_jitter()
```

From the scatter plot, we can see that there no relationship between the rating and cocoa percentage.

```{r}
choco_new <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(data = choco_new, aes(x = Company.Location, y = Rating, fill = Company.Location)) + 
  geom_boxplot()

```

From the boxplot we can see that all the countires have the same rating median. canada has heigest number in low.
